Verification of SE Formulas for Mediation Analysis

### 2024-05-01 notes/UQ Verification.tex
Binary response, binary mediator, fixed effects

@@

How does the standard error decompose between multiple responses with the same fixed covariates (i.e. $X$ and $W$), versus across replicated covariates? I can imagine how to do this, at least naively: do a bunch of analyses on each of a bunch of sets of covariates. Compute the average ``within-covariates'' variance and the average total variance. Compute the fraction of total variance due to response replication and, interestingly, one minus this fraction as a naive representation of the variance fraction due to covariate variability.

>>>>

I had to update Bruno's formulas. It looks like he forgot to include the $\bP(Y=1 | X=x, \mathbf{W}=\mathbf{w})$ term in the odds, and thus in the odds ratio. This has been changed now in the Overleaf document. I also worked out all the partial derivatives using Maple, which can produce \textit{Julia} (or \textit{R}, \textit{Python}) code to evaluate these horrendous expressions. All partials were validated against a simple finite difference approximation.

Table \ref{tab:SEs_bin_bin_fix} gives empirical and analytical SEs when $n=1000$.

\begin{table}
    \centering
    \begin{tabular}{|c|c|c|}
        \hline
        Empirical & Mean Analytical & Median Analytical\\
        \hline
        0.1060 & 0.1064 & 0.1062\\
        \hline
    \end{tabular}
    \caption{Standard errors for estimated mediation effect with binary response and mediation, fixed-effects.}
    \label{tab:SEs_bin_bin_fix}
\end{table}

@@

How does the standard error decompose between multiple responses with the same fixed covariates (i.e. $X$ and $W$), versus across replicated covariates? I can imagine how to do this, at least naively: do a bunch of analyses on each of a bunch of sets of covariates. Compute the average ``within-covariates'' variance and the average total variance. Compute the fraction of total variance due to response replication and, interestingly, one minus this fraction as a naive representation of the variance fraction due to covariate variability. \textbf{Every time I've checked this, the difference has been very small. This isn't a priority for me right now.}
